Discovery of $r$-process stars in LAMOST

### 2018-01-22 article/ms.tex
minor

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Research is fun, max. 45 characters]{You can't spell Euphoric without Eu.}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Matthew T. Miles et al.]{
Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
A. N. Other,$^{2}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country
}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Discovery of r-process stars in LAMOST]{Discovery of $r$-process stars in LAMOST}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Matthew T. Miles et al.]{Matthew T. Miles,$^{1}$\thanks{E-mail: mtmil3@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Brodie Norfolk?,$^{1}$
Alex Kemp?,$^{1}$\newauthor
John Lattanzio?,$^{1}$
Kevin Schlaufman?,$^{3}$
Alexander P. Ji?,$^{4}$
\emph{et al?}
\\
% List of institutions
$^{1}$School of Physics and Astronomy, Monash University, Clayton Campus, Victoria 3800, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton Campus, Victoria 3800, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA\\
$^{4}$Carnegie Observatories
}
